Stack Safety as a Security Property

### 2020-06-02 main.tex
Notes

Contributions:
\begin{itemize}
\item A formal property capturing the informal understanding of what ``stack safety'' is.
\item Evidence that this property really does capture the folk intuition: we show that the stack
  unsafe examples from the literature also fail our property.
\item Evidence that the property is not too strong. It's realizible by
  a previously proposed  micropolicy enforcement mechanism \leo{And it
    says yes on a substantial body of code}
\item A (inductive? step-by-step/stepwise) variant of this property
  tuned for testing/verification together with a proof that it implies
  the original property.  We test the whole thing with a cool
  framework.
\item A lazy version of the property that allows for more efficient/dynamic enforcement.
  Maybe testing.
\item TODO: Logic? Reasoning Principles?
\end{itemize}

@@

@@

>>>>

Contributions:
\begin{itemize}
\item A formal property capturing the informal understanding of what ``stack safety'' is.
\item Evidence that this property is strong enough to capture the folk
intuition: we show that the stack
  unsafe examples from the literature also fail our property.
\item Evidence that the property is not too strong. It's realizible by
  a previously proposed  micropolicy enforcement mechanism \leo{And it
    says yes on a substantial body of code}
\item A (inductive? step-by-step/stepwise) variant of this property
  tuned for testing/verification together with a proof that it implies
  the original property.  We test the whole thing with a cool
  framework.
\item A lazy version of the property that allows for more efficient/dynamic enforcement.
  Maybe testing.
\item TODO: Logic? Reasoning Principles?
\end{itemize}

@@

\section{Discussion}

\bcp{Illustrate the definition by using it to discuss a range of ``stack
  unsafety'' examples from the literature. }

@@

\section{Future Work}

We've assumed that callees always have less access than their callers, but
in real systems things are more complicated (because of objects, static
variables in C, software compartmentalization, coroutines, ...).  What we've
defined is a very ``pure'' variant of stack safety.  In future work, we
should go further. :-)
